---
title: "Trying to use DC3"
author: "Andy Tran"
date: "10 July 2020"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{scClassify}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

knitr::opts_chunk$set(fig.width=8, fig.height=6) 
```


# Import Necessary Packages

```{r, include = FALSE}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(Matrix)
library(pheatmap)
library(tictoc)
library(Rtsne)
library(SingleCellExperiment)
library(umap)
library(scater)
library(foreach)
library(doParallel)
```

Read in data
```{r}
A <- readRDS("Processed_matrices/A_processed_30-10-20.rds")
E <- readRDS("Processed_matrices/E_processed_30-10-20.rds")
C <- readRDS("Processed_matrices/C_processed_30-10-20.rds")
T_mat <- readRDS("Processed_matrices/T_processed_30-10-20.rds")
cell_types <- readRDS("Processed_matrices/celltypes_processed_30-10-20.rds")

E <- E[order(rownames(E)),]
C <- C[order(rownames(C)),]


rownames(A) <- colnames(C)
```

Set parameters
```{r}
P <- nrow(E)
Q <- nrow(A)
N <- ncol(E)
N_tfs <- nrow(T_mat)
table(cell_types$celltype)
```

Create H
```{r}
cell_type_names <- c("TAC-1", "TAC-2", "IRS", "Medulla", "Hair Shaft-cuticle.cortex")
K <- length(cell_type_names)
H <- matrix(nrow = N, ncol = K)

for(i in 1:K){
  H[,i] <- cell_types$celltype == cell_type_names[i]
}
H <- apply(H, 2,as.numeric)
rownames(H) <- cell_types$bc
colnames(H) <- cell_type_names
```




Set up SCE objects
```{r}
H_Dframe <- DataFrame(H)
H_Dframe@listData <- lapply(H_Dframe@listData, factor)
E_sce <- SingleCellExperiment(list(counts=E),
    colData=cbind(DataFrame(label=factor(cell_types$celltype),barcode=colnames(E)),H_Dframe),
    rowData=DataFrame(gene=rownames(E))
)

A_sce <- SingleCellExperiment(list(counts=A),
    colData=cbind(DataFrame(label=factor(cell_types$celltype),barcode=colnames(A)),H_Dframe),
    rowData=DataFrame(enhancer=rownames(A))
)

C_sce <- SingleCellExperiment(list(counts=C),
    colData=cbind(DataFrame(enhancer=colnames(C))),
    rowData=DataFrame(gene=rownames(C))
)

```

Check cell quality in E
```{r}
per.cell <- perCellQCMetrics(E_sce)
summary(per.cell$sum)
summary(per.cell$detected)

colData(E_sce) <- cbind(colData(E_sce), per.cell)
#plotColData(E_sce, x = "sum", y="detected", colour_by="label") 
```

Check cell quality in A
```{r}
per.cell <- perCellQCMetrics(A_sce)
summary(per.cell$sum)
summary(per.cell$detected)

colData(A_sce) <- cbind(colData(A_sce), per.cell)
# plotColData(A_sce, x = "sum", y="detected", colour_by="label") 

# keep_cell <- per.cell$detected >= 1
# A_sce <- A_sce[,keep_cell]
# E_sce <- E_sce[,keep_cell]
# H <- H[keep_cell,]
# embeddings <- embeddings[keep_cell,]

dim(A_sce)
dim(E_sce)
```

Check gene quality in E, remove genes expressed in <1% cells
```{r}
per.feat <- perFeatureQCMetrics(E_sce)
summary(per.feat$mean)
summary(per.feat$detected)
summary(nexprs(E_sce, byrow=TRUE))

keep_gene <- nexprs(E_sce, byrow=TRUE) >= N/100
E_sce <- E_sce[keep_gene,]
C_sce <- C_sce[keep_gene,]

dim(E_sce)
dim(C_sce)
```

Check Enhancer quality in C, remove enhancers that regulate 0 genes
```{r}
summary(nexprs(C_sce, byrow=FALSE))

keep_enhancer <- nexprs(C_sce, byrow=FALSE) >= 1
A_sce <- A_sce[keep_enhancer,]
C_sce <- C_sce[,keep_enhancer]
T_mat <- T_mat[,keep_enhancer]

dim(A_sce)
dim(C_sce)
dim(T_mat)
```

Check enhancer quality in A, keep enhancers that are accessible in 1% of cells.
```{r}
per.feat <- perFeatureQCMetrics(A_sce)
summary(per.feat$mean)
summary(per.feat$detected)
summary(nexprs(A_sce, byrow=TRUE))

keep_enhancer <- nexprs(A_sce, byrow=TRUE) >= N/100
A_sce <- A_sce[keep_enhancer,]
C_sce <- C_sce[,keep_enhancer]
T_mat <- T_mat[,keep_enhancer]

dim(A_sce)
dim(C_sce)
dim(T_mat)
```

Check gene quality in C, DO NOT remove genes expressed regulated by 0 enhancers
```{r}
summary(nexprs(C_sce, byrow=TRUE))

# keep_gene <- nexprs(C_sce, byrow=TRUE) >= 1
# E_sce <- E_sce[keep_gene,]
# C_sce <- C_sce[keep_gene,]

dim(E_sce)
dim(C_sce)
```

Final check
```{r}
summary(nexprs(E_sce, byrow=FALSE))
summary(nexprs(A_sce, byrow=FALSE))
summary(nexprs(C_sce, byrow=FALSE))
summary(nexprs(E_sce, byrow=TRUE))
summary(nexprs(A_sce, byrow=TRUE))
summary(nexprs(C_sce, byrow=TRUE))
```

Only keep TFs that survive
```{r}
tf_ind <- which(rownames(T_mat) %in% rownames(E_sce))
T_mat <- T_mat[tf_ind,]
dim(T_mat)
```

Check dimensions
```{r}
dim(A_sce)
dim(E_sce)
dim(C_sce)
dim(T_mat)
```

Check consistency
```{r}
identical(rownames(A_sce),colnames(C_sce))
identical(rownames(A_sce),colnames(T_mat))
identical(colnames(A_sce),colnames(E_sce))
identical(rownames(E_sce),rownames(C_sce))
```
Convert back to matrices
```{r}
A <- assay(A_sce)
E <- assay(E_sce)
C <- assay(C_sce)
```

```{r}
saveRDS(A, "Filtered_matrices/A_filtered_03-11-2020.rds")
saveRDS(E, "Filtered_matrices/E_filtered_03-11-2020.rds")
saveRDS(C, "Filtered_matrices/C_filtered_03-11-2020.rds")
saveRDS(T_mat, "Filtered_matrices/T_filtered_03-11-2020.rds")
saveRDS(H, "Filtered_matrices/H_filtered_03-11-2020.rds")
```

```{r}
sessionInfo()
```
